\section{Effective Actions and their 12d Consistencies}
The type IIB supergravity \eqref{Einstein frame IIB action} is understood as the low energy effective field theory of the type IIB string theory.
Under higher-derivative and stringy corrections, the SL(2, R) symmetry is believed to be broken to the discrete group SL(2, Z) \cite{Schwarz:1995dk}.
If the type IIB theory admits certain 12d interpretation, such interpretation, and its implications on effective actions, must be consistent with the type IIB effective action and SL(2, Z).

In this section, we review the current understandings in SL(2, Z) as arising from higher-derivative corrections, and their 12d interpretations.
We will begin by reviewing how one obtains higher-derivative corrections in supergravity from perturbative string theory, most importantly how the SL(2, Z) invariance arises non-perturbatively from the D(-1) backgrounds.
Then we discuss current understandings on 12d interpretations of SL(2, Z), and identify certain directions in advancing them. 
We conclude by discussing a potential parallel, between type IIA and type IIB, where the D0 and D(-1) backgrounds are effectively accounted for by loops of higher-dimensional KK modes.

\subsection{Recap: Perturbative String Theory and Higher-Derivative Supergravity}
{\color{orange}
The perturbative expansion of string amplitudes is organized by two parameters: $\alpha' = l_s^2$ controls the derivative expansion, and $g_s$ counts the genus of the string worldsheet in string path-integrals.
An $n$-point amplitude is a summation over worldsheet path-integrals of genus $g$
\begin{equation}
    \mathcal A_n(\alpha') = \sum_{g=0}^\infty g_s^{2g-2+n} \mathcal A_n^{(g)}(\alpha').
\end{equation}
}


The tree-level 4-point function in the type IIA and type IIB string theories is the Virasoro-Shapiro amplitude \cite{Green:2012oqa}, for the symmetric traceless massless modes in the NSNS sector of the string, they take the following form \cite{Green:1999pv} up to an irrelevant overall factor
\begin{equation}
\begin{aligned}
\mathcal A_4
&=\frac{\alpha^{\prime 4}}{3\cdot 2^3 g_s^2}
K
\times\frac{64}{\alpha^{\prime 3}stu}
\frac{\Gamma[1-\tfrac{\alpha'}{4}s]\Gamma[1-\tfrac{\alpha'}{4}t]\Gamma[1-\tfrac{\alpha'}{4}u]}{\Gamma[1+\tfrac{\alpha'}{4}s]\Gamma[1+\tfrac{\alpha'}{4}t]\Gamma[1+\tfrac{\alpha'}{4}u]}\\
K &\equiv t_8^{m_1...m_8}t_8^{n_1...n_8}               
\prod_{r=1}^4\zeta^{(r)}_{m_{2r}n_{2r}}k^{(r)}_{m_{2r-1}}k^{(r)}_{n_{2r-1}}
\end{aligned}
\end{equation}
where $s,t,u$ are Mandelstam variables, $\zeta^{(i)}_{mn}$ is the dimensionless polarization of the symmetric traceless modes on a closed string, they may also be interpreted as polarizations of the spacetime graviton $\kappa h^{(i)}_{mn}$ in $G_{mn}=\eta_{mn} + \kappa h_{mn}$. 
The explicit form of $t_8 t_8$ can be found in \cite{Schwarz:1982jn,Policastro:2008hg,Liu:2025uqu}.
Using the relation
\begin{equation}
\ln\Gamma(1-x)-\ln\Gamma(1+x) = 2\gamma x + 2\sum_{m\ge0}\frac{\zeta(2m+3)}{2m+3}x^{2m+3},
\end{equation}
we find the expansion
\begin{equation}
\mathcal{A}_4 = \frac{\alpha^{\prime 4}}{3\cdot 2^3 g_s^2}
K
\left[ \frac{64}{\alpha^{\prime 3}stu} + 2 \zeta(3)\right]
 + O(\alpha^{\prime 5})
\end{equation}
evaluated in the string frame metric with $G_{mn} |_{\infty} = \eta_{mn}$.
From the relation $G_{mn} = e^{\Phi/2}g_{mn}$, we see that the Einstein frame metric is not asymptotically flat: $g_{mn} |_{\infty} = g_s^{1/2}\eta_{mn}$.
To translate $\mathcal{A}_4$ into the Einstein frame, we need to translate implicit contractions with the string frame metric with those with the Einstein frame metric, which introduces factors of $g_s$.
The net effect is the following Einstein frame expansion
\begin{equation}
\mathcal{A}_4 \bigg|_{g_{mn}} = 
\frac{\alpha^{\prime 4}}{3\cdot 2^3 }
K
\times
\left[ \frac{64}{\alpha^{\prime 3}stu} + 2 \zeta(3)g_s^{-3/2}\right]
 + O(\alpha^{\prime 5}),
\end{equation}
with $\zeta_{mn}^{(r)}$ inside $K$ now interpreted as the polarization of the Einstein frame graviton and all contractions are implicitly performed with the asymptotic Einstein frame metric $g_s^{1/2}\eta_{mn}$.

The polynomial $K$ is analytic in the momenta and is the linear term in the expansion of $\frac{t_8 t_8 R^4}{16}$.
The nonlocal poles at $s, t, u = 0$ correspond to massless graviton exchange and reproduce the $s,t,u$-channel structure generated by the cubic graviton vertices of the Einstein-Hilbert action; the nonlocal $1/stu$ piece is therefore attributed to the tree-level supergravity dynamics.
Indeed it is accompanied by a single factor of $\alpha'$ which reveals its origin in the two-derivative supergravity.

The next contribution appears at $O(\alpha^{\prime 4}$) which reveals an 8-derivative spacetime origin:
\begin{equation}
\frac{\alpha^{\prime 4}}{3 \cdot 2^3} K 2 \zeta(3) g_s^{-3/2} \cong
\frac{\alpha^{\prime 4}}{3 \cdot 2^7} t_8t_8 R^4 (2 \zeta(3) g_s^{-3/2}) + O(\alpha^{\prime 5}).
\end{equation}
The next order correction comes from genus-1 amplitudes \cite{Green:1999pv}.
It is also common in both type IIA and IIB theories, and comes with the $t_8 t_8 R^4$ factor. 
Combining the genus-0 and genus-1 amplitudes, we have the local effective actions
\begin{equation}
\mathcal{A}_4 = -4\pi^7 (t_8 t_8 R^4)(\alpha')^4
\left[
2 \zeta(3)\tau_2^{3/2}
+\frac{2\pi^2}{3}\tau_2^{-1/2}
\right]
+O(\alpha^{\prime 5}).
\end{equation}
Non-renormalization theorems suggest the perturbative corrections to $R^4$ terminate here at one-loop \cite{Green:1997tv,Kehagias:1997cq}.
Note that $\mathcal{A}_4$ as given above no longer has SL(2, R) symmetry. 
In fact, the SL(2, R) symmetry of the type IIB supergravity is only present at the two-derivative level together with corrections that do not depend on $\tau$.
As soon as higher-derivative terms with non-trivial dependence on $\tau$ enter, SL(2, R) is explicitly broken.

In particular, the type IIB string path integral requires summing over the D(-1) backgrounds \eqref{D-1 background}.
The single and multi-charged D(-1) backgrounds give rise to non-perturbative $R^4$ corrections \cite{Green:1997tv,Kehagias:1997cq} of the form
\begin{equation}
\mathcal A_{D(-1)}\propto (\alpha')^4t_8t_8R^4\sum_{m,n\ge1}\left(\frac{m}{n^3}\right)^{1/2}
(e^{2\pi i mn\tau}+e^{-2\pi i mn\bar{\tau}})
\left(
1+\sum_{k=1}^\infty(4\pi mn\tau_2)^{-k}\frac{\Gamma[k-1/2]}{\Gamma[-k-1/2]k!}
\right).
\end{equation}
When combined with the genus-0 and genus-1 perturbative contributions, these D(-1) terms assemble into the modular-invariant, non-holomorphic Eisenstein series
\begin{equation}
\begin{aligned}
f_0(\tau,\bar\tau)
&=\sum_{(m,n)\neq(0,0)}\frac{\tau_2^{3/2}}{|m+n\tau|^3}\\
&=2\zeta(3)\tau_2^{3/2}+\frac{2\pi^2}{3}\tau_2^{-1/2}\\
&\quad+4\pi^{3/2}\sum_{m,n\ge1}\left(\frac{m}{n^3}\right)^{1/2}
(e^{2\pi i mn\tau}+e^{-2\pi i mn\bar{\tau}})
\left(
1+\sum_{k=1}^\infty(4\pi mn\tau_2)^{-k}\frac{\Gamma[k-1/2]}{\Gamma[-k-1/2]k!}
\right),
\end{aligned}
\end{equation}
thereby restoring the SL(2, Z) duality symmetry.

\subsection{12d Effective Corrections}
From our previous discussion, the type IIB 4-graviton effective action takes on the following schematic form \cite{Kehagias:1997cq,Green:1997tv}
\begin{equation}
L^{(3)} \propto f_0(\tau,\bar\tau)t_8t_8 R^4
\label{10d IIB 4-graviton effective action}
\end{equation}
The rest of the 4-point effective action consists of axio-dilaton and is SL(2, Z) invariant, they can be found in \cite{Policastro:2006vt,Policastro:2008hg}
To produce the 10d effective action \eqref{10d IIB 4-graviton effective action},
a ``12d effective action" had been proposed as \cite{Minasian:2015bxa} 
\begin{equation}
\hat{L}^{(3)} \propto f_0(\tau,\bar\tau)t_8t_8 \hat{R}^4,
\label{eq:liu-12d-ansatze}
\end{equation}
where $\hat{R}$ is the 12d Riemann tensor computed with $\hat{g}_{MN}$, as in \eqref{12d metric ansatz}
It was shown that \eqref{eq:liu-12d-ansatze} reduced on the 12d metric ansatz  produces, at 4-point, the effective action in the axio-dilaton sector \cite{Policastro:2006vt,Policastro:2008hg}.
However, it was later shown that \eqref{eq:liu-12d-ansatze} is inconsistent with 10d type IIB amplitudes at 5-point \cite{Liu:2025uqu}.

We now comment on certain limitations of the proposed 12d effective action \eqref{eq:liu-12d-ansatze} and outline possible directions forward.
First, $\epsilon_{10}\epsilon_{10}R^4$ vanishes at 4-point, so the result of \cite{Minasian:2015bxa} on $\epsilon_{10}\epsilon_{10}R^4$ was that $\varepsilon_{12}\varepsilon_{12}\mathcal R^4$ vanishes at 4-point as well, after reducing $\mathcal G_{MN}$ to $g_{mn},\phi,C$.
The correspondence would be significantly stronger if non-vanishing components of $\epsilon_{10}\epsilon_{10}R^4$ could be verified, e.g. for 5-point amplitudes.
Unfortunately, this does not occur \cite{Liu:2025uqu}.

A second issue concerns the interpretation of the $t_8t_8 R^4$ term.
The $t_8$ tensor is originally defined by traces over the gamma matrices of SO(8) \cite{Schwarz:1982jn}, which is the little group of SO(9, 1).
Accordingly, the kinematic structure encoded by $t_8t_8R^4$ is that of the 8d space transverse to a massless momentum.
In the 4-graviton amplitude, the kinematic structure of $t_8t_8 R^4$ is thus determined solely by the 8 transverse components of the graviton polarizations and momenta, rather than all 10.
For example, one is able to extract $t_8t_8 R^4$ from 9d amplitudes obtained by compactifying M-theory on a torus \cite{Green:1997as}.
Consequently, when examining non-vanishing 4-graviton $t_8t_8R^4$ amplitudes, it is ambiguous whether one is investigating the established relation between 11d and 9d, or between 12d and 10d.
By contrast, $\epsilon_{10}\epsilon_{10}R^4$ is intrinsically 10d.
Thus, to strengthen the proposed relation between 12d and 10d amplitudes, it is worth investigating how one may capture $\epsilon_{10}\epsilon_{10}R^4$ from 12d.

Lastly, from a geometric perspective,in 12d $\tau$ should not explicitly appear. 
The point in repackaging the type IIB theory and its corrections in a 12d-covariant way is to geometrize $\tau$ as part of the metric, so one should be alarmed to find the need to put in SL(2, Z) covariance by hand, e.g. via $f_0(\tau,\bar\tau)$.
Perhaps a more appropriate 12d amplitude would be
\begin{equation}
\hat{L}^{(3)} \propto f(\hat{g}_{MN},\hat{R}_{MNPQ}).
\end{equation}
Then upon reduction on a torus, 2 of the 12 directions are singled out, we are thus able to distinguish $\tau$ from the rest of the metric, and obtain the modular function and $R^4$
\begin{equation}
f(\hat{g}_{MN},\hat{R}_{MNPQ})
= f_0(\tau,\bar\tau)(t_8t_8 + \epsilon_{10}\epsilon_{10})R^4 + ....
\end{equation}
This alternative route may be worth exploring, but at the moment it is not clear how to construct such $f(\hat{g},\hat{R})$, and the ansatze of \cite{Minasian:2015bxa} remains the most natural choice.
One may look into functions that admit expansions over $f_0$, or consider possible 12d interpretations of the IIB 5-point amplitudes.
The type IIB amplitudes, starting at 5-points, famously contain the ``U(1)-violating terms" \cite{Liu:2025uqu}. This is one clear obstruction to extending the 12d ansatze of \eqref{eq:liu-12d-ansatze}.
It would also be illuminating to elucidate how this obstruction shall be interpreted, or worked around, in 12d.
Alternatively, one may still hope that certain 12d tensor contraction structure could capture the kinematics of 10d amplitudes, as constrained by SL(2, Z), and be content with a separate ansatze for the U(1)-violating sectors.





\subsection{KK-modes and D-brane Backgrounds}
Previously we argued that the type IIB effective action at 5-point is critical in validating the 12d repackaging of the 10d effective actions.
The significance of the 5-point amplitudes is further elevated in a separate but closely related context of the type IIB effective actions, namely the role of the supergravity KK-modes as an effective repackaging of the D0 and D(-1) backgrounds in string path integrals. 

We begin in 12d, with coordinates ($x^\mu,y^1,y^2)$, after identifying
\begin{equation}
y^1\to y^1+2\pi R,\quad
(y^1,y^2)\to (y^1+2\pi R\tau_1,y^2+2\pi R\tau_2)
\end{equation}
for some radius $R$, we can Fourier expand a scalar in 12d on $T_2$:
\begin{equation}
\Phi(x^\mu,y^1,y^2)
=\sum_{m,n}\Phi_{m,n}(x^\mu) \times\exp
\left[
\frac{i}{R\tau_2}\left(m\tau_2y^1 + (n-m\tau_1)y^2\right)
\right].
\end{equation}
The massive modes are
\begin{equation}
[-\nabla^2_{10}-\nabla^2_2]\phi_{p,m,n}
=\left(p_{10}^2+M_{m,n}^2\right)\phi_{p,m,n},\quad
M^2_{m,n} 
= \frac{m^2}{R^2}+\frac{(n-m\tau_1)^2}{R^2\tau_2^2}
=\frac{|n-m\tau|^2}{R^2\tau_2^2}.
\end{equation}
For 4-point amplitudes in 10d, we may evaluate contributions from loops of the infinite tower of massive KK-modes using Schwinger proper time
\cite{Green:1997as,Beccaria:2023hhi}
\begin{equation}
\begin{aligned}
\mathcal{A}_4
\propto \sum_{n,m}\int_{\Lambda^{-2}}^\infty
\frac{d\lambda}{\lambda^{3/2}}
e^{-\lambda \frac{|n+m\tau|^2}{R^2\tau_2^2}}
P(s,t;\lambda),\quad
P(s,t;\lambda)
=\int_0^1d\rho_3 \int_0^{\rho_3}d\rho_2\int_0^{\rho_2} d\rho_1e^{-\tau M(s,t;\rho)},\\
M(s,t;\rho)=s\rho_1\rho_2+t\rho_2\rho_3+u\rho_1\rho_3 + t(\rho_1-\rho_2),\quad
s+t+u=0.
\end{aligned}
\label{4-point Schwinger parameter}
\end{equation}
To evaluate $\mathcal{A}_4$ above, one performs Poisson resummations followed by zeta-function renormalization, and a low-energy expansion over $s,t,u$.
But there is a shortcut of adding a spectator dimension to known results of 11d amplitudes on a torus \cite{Green:1997as}.
Either way, one finds
\begin{equation}
\begin{aligned}
\mathcal{A}_4
&\propto  f_0(\tau,\bar\tau)(s^2+t^2+u^2)+...\\
&\sim f_0(\tau,\bar\tau)t_8t_8R^4+....
\end{aligned}
\end{equation}
Viewed from string theory, this is the effective action at genus-1 with the D(-1) background.
In other words, the tower of KK-modes on a torus acts as a surrogate for the D(-1) background.
This is in parallel with the 10d type IIA supergravity, where the KK modes on $S_1$ running in a loop produce the D0 background in the type IIA strings \cite{Green:1997as}.

We do not wish to overclaim.
The point we are making is that what used to be a relation between 11d and 9d \cite{Green:1997as} is perfectly compatible with that between 12d and 10d.
But this might just arise from $t_8t_8 R^4$ not being an intrinsically 10d term.
It is worth exploring amplitudes that clearly signal 10d momenta, e.g. $\epsilon_{10}\epsilon_{10}R^4$ at 5-point.
One may attempt to evaluate KK-loop contributions to 5-point amplitudes, using the 5-point Schwinger proper time formula analogous to \eqref{4-point Schwinger parameter}, as given in \cite{Minasian:2015bxa,Green:1999by,Liu:2022bfg}.