\section{The D3 Brane and Self-Duality}
\label{sec:d3-self-duality}
The low-energy dynamics of a D3 brane in a given type IIB supergravity background are described by the Dirac-Born-Infeld action supplemented by a Wess-Zumino term, with background metric, NSNS and RR fields entering through the appropriate pullbacks to the brane worldvolume \cite{Leigh:1989jq,Polchinski:1998rr}.
In particular, in Einstein frame the bosonic sector of the D3 low-energy action takes the form \cite{Tseytlin:1996it}
\begin{equation}
\begin{aligned}
S_{D3}
&=\int d^4x \sqrt{-\det\big({g}_{mn} + e^{-\Phi/2} (\mathcal{F}_2)_{mn}\big)}\\
&\quad+\int \Big(C_4 + C_2\wedge \mathcal{F}_2 + \tfrac{1}{2} C_0 \mathcal{F}_2\wedge\mathcal{F}_2\Big)
+\text{higher order},\qquad
\mathcal{F}_2 \equiv dA_1+B_2 .
\end{aligned}
\label{D3-action}
\end{equation}
Throughout, the bulk supergravity fields are understood to be pulled back onto the brane worldvolume, where $m,n$ label worldvolume indices, $(\mathcal{F}_2)_{mn}$ are the components of the worldvolume 2-form $\mathcal{F}_2$, and $C_0$ is the RR axion.
The vector $A_m$ is the dynamical gauge potential on the brane worldvolume.
It was shown \cite{Tseytlin:1996it} that the action is invariant under electromagnetic duality only if the bulk background simultaneously undergoes an \SLZ{} transformation.
We derive this explicitly below.

To quadratic order in $\mathcal F_2$ the gauge sector of \eqref{D3-action} reads, in the notation of differential forms,
\begin{equation}
\int\left[\tfrac{1}{2}e^{-\Phi}\mathcal F_2\wedge\star\mathcal F_2+\tfrac{1}{2}C_0\mathcal F_2\wedge\mathcal F_2+C_2\wedge\mathcal F_2\right],\qquad \mathcal F_2 = dA_1+B_2.
\end{equation}
To dualise, we promote $\mathcal F_2$ to an independent field and add a Lagrange multiplier 
\begin{equation}
\tilde{F}_2 \wedge (\mathcal{F}_2 - B_2)
\end{equation}
to enforce $d(\mathcal F_2-B_2) = 0$, where $\tilde F_2 = d\tilde A_1$ is the field strength of the dual potential $\tilde A_1$.
Varying the now-independent $\mathcal F_2$ instead gives the algebraic relation
\begin{equation}
(e^{-\Phi}\star + C_0)\mathcal F_2 = -(\tilde F_2+C_2).
\label{D3-integrating-out-mathcal-F}
\end{equation}
We now integrate $\mathcal F_2$ out and ask whether the resultant D3 action is in the form \eqref{D3-action}, with $d\tilde A_1$ in place of $dA_1$. 
Using $\star^2=-1$, we have
\begin{equation}
(C_0+e^{-\Phi}\star)^{-1} = \frac{C_0-e^{-\Phi}\star}{C_0^2+e^{-2\Phi}},
\end{equation}
so \eqref{D3-integrating-out-mathcal-F} solves to $\mathcal F_2 = -\dfrac{C_0-e^{-\Phi}\star}{C_0^2+e^{-2\Phi}}(\tilde F_2+C_2)$. Substituting back, the gauge sector becomes the same Maxwell form for the dual field strength $\tilde F_2+C_2$, with the coupling inverted to $\tau'\equiv C_0'+ie^{-\Phi'}=-1/\tau$:
\begin{equation}
\begin{aligned}
\int\bigg[&\tfrac{1}{2}e^{-\Phi'}(\tilde F_2+C_2)\wedge\star(\tilde F_2+C_2)\\
&+\tfrac{1}{2}C_0'(\tilde F_2+C_2)\wedge(\tilde F_2+C_2)-\tilde F_2\wedge B_2\bigg].
\end{aligned}
\end{equation}
We read off that this is in the same form as the D3 action \eqref{D3-action}, with $\tilde A_1$ in place of $A_1$, provided we make the following field redefinitions
\begin{equation}
\tau\to-\frac{1}{\tau},\qquad
B_2 \to C_2,\qquad C_2\to -B_2.
\end{equation}
This is precisely the $S$ generator of the type IIB bulk \SLZ{} duality.
Because the D3 action is also invariant under the axion shift $C_0\to C_0+1$, the full \SLZ{} duality is realised on the D3 worldvolume.
% The nonlinear Born-Infeld terms do not affect this conclusion: the Born-Infeld determinant is invariant under the Legendre transform \cite{Tseytlin:1996it}, so the full action \eqref{D3-action} returns to its original form under this transformation.
The bulk generator $T: \tau\to \tau+1$ corresponds to $\theta\to \theta + 2\pi$ on the D3 worldvolume, for the complexified coupling $\tau_{YM}\equiv \frac{\theta}{2\pi} + \frac{4\pi i}{g^2}$.
Thus the \SLZ{} duality of $\mathcal N=4$ SYM on the D3 worldvolume is intimately linked to the type IIB \SLZ{} duality, with the bulk $S$ generator realised as the worldvolume electromagnetic duality.

For comparison, we recall a similar story on the type IIA side.
The analogy is not direct because there is no analogue of the \SLZ{} duality in the type IIA theory.
The D2 action can be written in string frame as \cite{Schmidhuber:1996fy,Tseytlin:1996it}
\begin{equation}
S_{D2}
=\int d^3x \sqrt{-e^{-2\Phi}\det (G_{mn}+(\mathcal F_2)_{mn})}
+\int\left(C_3-C_1\wedge\mathcal F_2\right),\qquad
\mathcal F_2\equiv dA_1-B_2.
\end{equation}
We dualise the worldvolume vector into a scalar, paralleling the D3 treatment.
We promote $\mathcal F_2$ to an independent field and enforce $dd A_1 = 0$ through a Lagrange multiplier, here a scalar $y$,
\begin{equation}
\int dy\wedge(\mathcal F_2 + B_2).
\end{equation}
Trading the independent $\mathcal F_{mn}$ for its dual vector through $\mathcal F_{mn}=\epsilon_{mnp}v^p$, so that $\tfrac12\mathcal F_{mn}\mathcal F^{mn}=-v_pv^p$, the action becomes%
\footnote{In three dimensions the Born-Infeld determinant collapses: for antisymmetric $\mathcal F_{mn}$ one has $\det(G_{mn}+\mathcal F_{mn})=\det G_{mn}(1+\tfrac12\mathcal F_{mn}\mathcal F^{mn})$, so the DBI term equals $e^{-\Phi}\sqrt{-G}\sqrt{1+\tfrac12\mathcal F_{mn}\mathcal F^{mn}}$.}
\begin{equation}
S_{D2}=\int d^3x\sqrt{-G}\left[e^{-\Phi}\sqrt{1-v_pv^p}-(C_1-dy)_pv^p\right]+\int\left(C_3 + B_2\wedge dy\right).
\end{equation}
Integrating out $v$ using its algebraic equation of motion
\begin{equation}
\frac{e^{-\Phi}v_p}{\sqrt{1-v_qv^q}}=-(C_1-dy)_p,
\label{D2-integrating-out-v}
\end{equation}
we find
\begin{equation}
S_{D2}=\int d^3x\sqrt{-G}\sqrt{e^{-2\Phi}+(C_1-dy)_p(C_1-dy)^p}+\int\left(C_3 + B_2\wedge dy\right).
\end{equation}
Finally, the rank-one identity $\det(aG_{mn}+bK_mK_n)=a^3\det G_{mn}(1+\tfrac{b}{a}K_pK^p)$ with $a=e^{-2\Phi/3}$, $b=e^{4\Phi/3}$ repackages the integrand into a single determinant,
\begin{equation}
\begin{aligned}
S_{D2}
&=\int d^3x\sqrt{-\det\big(e^{-2\Phi/3}G_{mn} + e^{4\Phi/3}(C_1-dy)_m(C_1-dy)_n\big)}\\
&\quad+ \int\left(C_3 + B_2\wedge dy\right).
\end{aligned}
\end{equation}
Then as one interprets the worldvolume scalar $y$ as a 10d scalar pulled back onto the D2 worldvolume, this is the M2 action directly reduced on $S^1$ \cite{Bergshoeff:1987cm,Tseytlin:1996it,Schmidhuber:1996fy}. The bracketed metric is the standard Kaluza-Klein form, and $C_3+B_2\wedge dy$ is the reduction of the 11d three-form.

Just as the M2 brane reduced on a circle gives the D2, one could speculate that the D3 arises from some 12d brane reduced on a two-torus $T^2$.
A two-torus is built from two circles, and its shape (their relative size and tilt) is captured by a single complex number $\tau$.
Different choices of which two loops to call the basic cycles are physically equivalent, and passing between them changes $\tau$ by \SLZ{} transformations such as $\tau\to-1/\tau$, leaving the torus itself untouched.
This is precisely how the \SLZ{} we found acts on the IIB axio-dilaton, and hence, through the dualisation above, on the gauge coupling $\tau_{YM}$ of $\mathcal{N}=4$ SYM on the D3 worldvolume.

Suppose there exists a certain 5-brane in 12d, which has its own worldvolume gauge theory.
Wrapping such a 5-brane on $T^2$ parametrised by $\tau$ would give a 3-brane in 10d.
The worldvolume gauge theory of the resultant 3-brane would be related to the modulus $\tau$ of the torus, and \SLZ{} transformations on such $\tau$ would result in duality transformations on the worldvolume gauge theory, as we have seen in the D3 case.
The same logic applies to a hypothetical 3-brane in 12d, since the pullback of the 12d metric would enter its worldvolume action, and the \SLZ{} transformations on the torus modulus $\tau$ would then induce a duality transformation on its worldvolume as well.

Whether such a torus is really present remains an open question, and a closer look at the D3's degrees of freedom shows why it is not straightforward.
A naive count of degrees of freedom is encouraging: a 3-brane in 12d has eight transverse directions, and the D3 worldvolume theory carries exactly eight bosonic degrees of freedom, six from its scalars and two from the vector field.
However, the two vector degrees of freedom are difficult to interpret as embedding coordinates.
One can wrap the D3 on a circle so that its worldvolume vector decomposes into two scalars \cite{Jatkar:1996np,Kar:1997cx}, but this simply reproduces the standard relation between M-theory on $T^2$ and 9d supergravity \cite{Green:1997as}.


