\section{Effective Actions and their 12d Consistencies}
The type IIB supergravity \eqref{Einstein frame IIB action} is understood as the low energy effective field theory of the type IIB string theory.
Under higher-derivative and stringy corrections, the SL(2, R) symmetry is believed to be broken to the discrete group SL(2, Z) \cite{Schwarz:1995dk}.
If the type IIB theory admits certain 12d interpretation, such interpretation, and its implications on effective actions, shall be consistent with the type IIB effective action and SL(2, Z).

In this section, we review the current understandings in SL(2, Z) as arising from higher-derivative corrections, and their 12d interpretations.
We will begin by reviewing how one obtains higher-derivative corrections in supergravity from perturbative string theory, most importantly how the SL(2, Z) invariance arises non-perturbatively from the D(-1) backgrounds.
We then discuss a potential parallel, between type IIA and type IIB, where the D0 and D(-1) backgrounds are effectively accounted for by loops of higher-dimensional KK modes.
We conclude by discussing how certain higher-derivative corrections of the type IIB axio-dilaton sector can be written in a 12d covariant form, and the limitations of such an interpretation.

\subsection{Recap: Perturbative String Theory and Higher-Derivative Supergravity}
{\color{orange}
The perturbative expansion of string amplitudes is organized by two parameters: $\alpha' = l_s^2$ controls the derivative expansion, and $g_s$ counts the genus of the string worldsheet in string path-integrals.
An $n$-point amplitude is a summation over worldsheet path-integrals of genus $g$
\begin{equation}
    \mathcal A_n(\alpha') = \sum_{g=0}^\infty g_s^{2g-2} \mathcal A_n^{(g)}(\alpha').
\end{equation}
}


The tree-level 4-point function in the type IIA and type IIB string theories is the Virasoro-Shapiro amplitude \cite{Green:2012oqa}, for the symmetric traceless massless modes in the NSNS sector of the string, they take the following form \cite{Green:1999pv} up to an irrelevant overall factor
\begin{equation}
\begin{aligned}
\mathcal A_4
&=\frac{\alpha^{\prime 4}}{3\cdot 2^3 g_s^2}
K
\times\frac{64}{\alpha^{\prime 3}stu}
\frac{\Gamma[1-\tfrac{\alpha'}{4}s]\Gamma[1-\tfrac{\alpha'}{4}t]\Gamma[1-\tfrac{\alpha'}{4}u]}{\Gamma[1+\tfrac{\alpha'}{4}s]\Gamma[1+\tfrac{\alpha'}{4}t]\Gamma[1+\tfrac{\alpha'}{4}u]}\\
K &\equiv t_8^{m_1...m_8}t_8^{n_1...n_8}               
\prod_{r=1}^4\zeta^{(r)}_{m_{2r}n_{2r}}k^{(r)}_{m_{2r-1}}k^{(r)}_{n_{2r-1}}
\end{aligned}
\end{equation}
where $s,t,u$ are Mandelstam variables, $\zeta^{(i)}_{mn}$ is the dimensionless polarization of the symmetric traceless modes on a closed string, they may also be interpreted as polarizations of the spacetime graviton $\kappa h^{(i)}_{mn}$ in $G_{mn}=\eta_{mn} + \kappa h_{mn}$. 
The explicit form of $t_8 t_8$ can be found in \cite{Schwarz:1982jn,Policastro:2008hg,Liu:2025uqu}.
Using the relation
\begin{equation}
\ln\Gamma(1-x)-\ln\Gamma(1+x) = 2\gamma x + 2\sum_{m\ge0}\frac{\zeta(2m+3)}{2m+3}x^{2m+3},
\end{equation}
we find the expansion
\begin{equation}
\mathcal{A}_4 = \frac{\alpha^{\prime 4}}{3\cdot 2^3 g_s^2}
K
\left[ \frac{64}{\alpha^{\prime 3}stu} + 2 \zeta(3)\right]
 + O(\alpha^{\prime 5})
\end{equation}
evaluated in the string frame metric with $G_{mn} |_{\infty} = \eta_{mn}$.
From the relation $G_{mn} = e^{\Phi/2}g_{mn}$, we see that the Einstein frame metric is not asymptotically flat: $g_{mn} |_{\infty} = g_s^{-1/2}\eta_{mn}$.
To translate $\mathcal{A}_4$ into the Einstein frame, we need to translate implicit contractions with the string frame metric with those with the Einstein frame metric, which introduces factors of $g_s$.
The net effect is the following Einstein frame expansion
\begin{equation}
\mathcal{A}_4 \bigg|_{g_{mn}} = 
\frac{\alpha^{\prime 4}}{3\cdot 2^3 }
K
\times
\left[ \frac{64}{\alpha^{\prime 3}stu} + 2 \zeta(3)g_s^{-3/2}\right]
 + O(\alpha^{\prime 5}),
\end{equation}
with $\zeta_{mn}^{(r)}$ inside $K$ now interpreted as the polarization of the Einstein frame graviton and all contractions are implicitly performed with the asymptotic Einstein frame metric $g_s^{-1/2}\eta_{mn}$.

The polynomial $K$ is analytic in the momenta and is the linear term in the expansion of $\frac{t_8 t_8 R^4}{16}$.
The nonlocal poles at $s, t, u = 0$ correspond to massless graviton exchange and reproduce the $s,t,u$-channel structure generated by the cubic graviton vertices of the Einstein-Hilbert action; the nonlocal $1/stu$ piece is therefore attributed to the tree-level supergravity dynamics.
Indeed it is accompanied by a single factor of $\alpha'$ which reveals its origin in the two-derivative supergravity.

The next contribution appears at $O(\alpha^{\prime 4})$ which reveals an 8-derivative spacetime origin:
\begin{equation}
\frac{\alpha^{\prime 4}}{3 \cdot 2^3} K 2 \zeta(3) g_s^{-3/2} \cong
\frac{\alpha^{\prime 4}}{3 \cdot 2^7} t_8t_8 R^4 (2 \zeta(3) g_s^{-3/2}) + O(\alpha^{\prime 5}).
\end{equation}
The next order correction comes from genus-1 amplitudes \cite{Green:1999pv}.
It is also common in both type IIA and IIB theories, and comes with the $t_8 t_8 R^4$ factor. 
Combining the genus-0 and genus-1 amplitudes, we have the local effective action
\begin{equation}
\mathcal{A}_4 = -4\pi^7 (t_8 t_8 R^4)(\alpha')^4
\left[
2 \zeta(3)\tau_2^{3/2}
+\frac{2\pi^2}{3}\tau_2^{-1/2}
\right]
+O(\alpha^{\prime 5}).
\end{equation}
Non-renormalization theorems suggest the perturbative corrections to $R^4$ terminate here at one-loop \cite{Green:1997tv,Kehagias:1997cq}.
Note that $\mathcal{A}_4$ as given above no longer has SL(2, R) symmetry. 
In fact, the SL(2, R) symmetry of the type IIB supergravity is only present at the two-derivative level together with corrections that do not depend on $\tau$.
As soon as higher-derivative terms with non-trivial dependence on $\tau$ enter, SL(2, R) is explicitly broken.

In particular, the type IIB string path integral requires summing over the D(-1) backgrounds \eqref{D-1 background}.
The single and multi-charged D(-1) backgrounds give rise to non-perturbative $R^4$ corrections \cite{Green:1997tv,Kehagias:1997cq} of the form
\begin{equation}
\mathcal A_{D(-1)}\propto (\alpha')^4t_8t_8R^4\sum_{m,n\ge1}\left(\frac{m}{n^3}\right)^{1/2}
(e^{2\pi i mn\tau}+e^{-2\pi i mn\bar{\tau}})
\left(
1+\sum_{k=1}^\infty(4\pi mn\tau_2)^{-k}\frac{\Gamma[k-1/2]}{\Gamma[-k-1/2]k!}
\right).
\end{equation}
When combined with the genus-0 and genus-1 perturbative contributions, these D(-1) terms assemble into the modular-invariant, non-holomorphic Eisenstein series
\begin{equation}
\begin{aligned}
f_0(\tau,\bar\tau)
&=\sum_{(m,n)\neq(0,0)}\frac{\tau_2^{3/2}}{|m+n\tau|^3}\\
&=2\zeta(3)\tau_2^{3/2}+\frac{2\pi^2}{3}\tau_2^{-1/2}\\
&\quad+4\pi^{3/2}\sum_{m,n\ge1}\left(\frac{m}{n^3}\right)^{1/2}
(e^{2\pi i mn\tau}+e^{-2\pi i mn\bar{\tau}})
\left(
1+\sum_{k=1}^\infty(4\pi mn\tau_2)^{-k}\frac{\Gamma[k-1/2]}{\Gamma[-k-1/2]k!}
\right),
\end{aligned}
\end{equation}
thereby restoring the SL(2, Z) duality symmetry.

\subsection{KK-modes and D-brane Backgrounds}
We saw above how summing over the D(-1) backgrounds completes the perturbative $R^4$ corrections into the Eisenstein series $f_0(\tau,\bar\tau)$, thereby restoring SL(2, Z).
Before turning to the 12d repackaging of the effective action, we point out a closely related observation: the supergravity KK-modes on a torus act as an effective repackaging of the D0 and D(-1) backgrounds in string path integrals.

We begin in 12d, with coordinates ($x^\mu,y^1,y^2)$, after identifying
\begin{equation}
y^1\to y^1+2\pi R,\quad
(y^1,y^2)\to (y^1+2\pi R\tau_1,y^2+2\pi R\tau_2)
\end{equation}
for some radius $R$, we can Fourier expand a scalar in 12d on $T_2$:
\begin{equation}
\Phi(x^\mu,y^1,y^2)
=\sum_{m,n}\Phi_{m,n}(x^\mu) \times\exp
\left[
\frac{i}{R\tau_2}\left(m\tau_2y^1 + (n-m\tau_1)y^2\right)
\right].
\end{equation}
The massive modes are
\begin{equation}
[-\nabla^2_{10}-\nabla^2_2]\phi_{p,m,n}
=\left(p_{10}^2+M_{m,n}^2\right)\phi_{p,m,n},\quad
M^2_{m,n}
= \frac{m^2}{R^2}+\frac{(n-m\tau_1)^2}{R^2\tau_2^2}
=\frac{|n-m\tau|^2}{R^2\tau_2^2}.
\end{equation}
For 4-point amplitudes in 10d, we may evaluate contributions from loops of the infinite tower of massive KK-modes using Schwinger proper time
\cite{Green:1997as,Beccaria:2023hhi}
\begin{equation}
\begin{aligned}
\mathcal{A}_4
\propto \sum_{n,m}\int_{\Lambda^{-2}}^\infty
\frac{d\lambda}{\lambda^{3/2}}
e^{-\lambda \frac{|n-m\tau|^2}{R^2\tau_2^2}}
P(s,t;\lambda),\quad
P(s,t;\lambda)
=\int_0^1d\rho_3 \int_0^{\rho_3}d\rho_2\int_0^{\rho_2} d\rho_1e^{-\lambda M(s,t;\rho)},\\
M(s,t;\rho)=s\rho_1\rho_2+t\rho_2\rho_3+u\rho_1\rho_3 + t(\rho_1-\rho_2),\quad
s+t+u=0.
\end{aligned}
\label{4-point Schwinger parameter}
\end{equation}
To evaluate $\mathcal{A}_4$ above, one performs Poisson resummations followed by zeta-function renormalization, and a low-energy expansion over $s,t,u$.
But there is a shortcut of adding a spectator dimension to known results of 11d amplitudes on a torus \cite{Green:1997as}.
Either way, one finds
\begin{equation}
\begin{aligned}
\mathcal{A}_4
&\propto  f_0(\tau,\bar\tau)(s^2+t^2+u^2)+...\\
&\sim f_0(\tau,\bar\tau)t_8t_8R^4+....
\end{aligned}
\end{equation}
Viewed from string theory, this is the effective action at genus-1 with the D(-1) background.
In other words, the tower of KK-modes on a torus acts as a surrogate for the D(-1) background.
This is in parallel with the 10d type IIA supergravity, where the KK modes on $S_1$ running in a loop produce the D0 background in the type IIA strings \cite{Green:1997as}.

We do not wish to overclaim.
The point we are making is that what used to be a relation between 11d and 9d \cite{Green:1997as} is perfectly compatible with that between 12d and 10d.
But this might just arise from $t_8t_8 R^4$ not being an intrinsically 10d term.
It is worth exploring amplitudes that clearly signal 10d momenta, e.g. $\epsilon_{10}\epsilon_{10}R^4$ at 5-point.
One may attempt to evaluate KK-loop contributions to 5-point amplitudes, using the 5-point Schwinger proper time formula analogous to \eqref{4-point Schwinger parameter}, as given in \cite{Minasian:2015bxa,Green:1999by,Liu:2022bfg}.

\subsection{12d Effective Corrections}
We begin by reviewing the known relations between type IIB and 12d, using a somewhat more general ``bottom-up" approach.
The type IIB axio-dilaton action, at the two-derivative level, can be written as
\begin{equation}
2\kappa^2 S_{IIB,\tau}
= \int d^{10}x \sqrt{-g} \left(R - 2 P_m \overline{P}^m\right).
\label{eq:IIB-two-derivative}
\end{equation}
where $P_m \equiv \frac{i\nabla_m \tau}{2\tau_2}$, and $\tau = \tau_1 + i \tau_2 = C_0 + i e^{-\Phi}$ is the axio-dilaton.

The proposal of F-theory \cite{Vafa:1996xn} is that for backreacted 7-brane configurations, the axio-dilaton profile $\tau$ can be geometrized as the complex structure of an auxiliary torus.
This proposal can be understood by noting that the 10d axio-dilaton action can be obtained by certain 12d action on a specific metric ansatze, where the 12d metric is given by
\begin{equation}
\widehat{g}_{MN}=\begin{pmatrix}
g_{mn} & 0 \\
0 &\widehat{g}_{ab}
\end{pmatrix},\quad
\widehat{g}_{ab}
=\frac{1}{\tau_2}\begin{pmatrix}
1& \tau_1\\
\tau_1 & \tau_1^2+\tau_2^2
\end{pmatrix}.
\label{eq:F-theory-ansatze}
\end{equation}
One may adopt complex tangent frame coordinates $z, \overline{z}$, with vielbein $e_{\alpha}{}^a = \frac{1}{2\sqrt{\tau_2}}\begin{pmatrix}
    -\tau & 1 \\ -\overline{\tau} & 1
\end{pmatrix}$, the nonvanishing components of the 12d Riemann tensor are \cite{Liu:2025uqu}
\begin{equation}
\widehat{R}_{mrns} = R_{mrns},\quad
R_{z\overline{z}z\overline{z}} = -\frac14 |P|^2,\quad
R_{mnz\overline{z}} = P_{[m}\overline{P}_{n]},\quad
R_{mzn\overline{z}} = - \frac{P_m \overline{P}_n}{2}\quad
R_{mznz} = \frac{D_m P_n}{2}.
\label{eq:12d-Riemann-complex}
\end{equation}
Substituting $P_m\overline{P}_n$ in \eqref{eq:IIB-two-derivative} with $R_{mzn\overline{z}}$, we find
\begin{equation}
\sqrt{-g}[R - 2 P_m \overline{P}^m]
=\sqrt{-\widehat{g}}[R + \widehat{R}^{mz}{}_{mz} + \widehat{R}^{m\overline{z}}{}_{m\overline{z}}]
=\sqrt{-\widehat{g}} \widehat{R},
\label{eq:2-derivative-index-splitting}
\end{equation}
which verifies that the F-theory ansatze \eqref{eq:F-theory-ansatze} relates the 10d axio-dilaton action to a 12d Einstein-Hilbert term.
Hence we may map solutions of 12d Einstein gravity, such as the pp-wave \cite{Tseytlin:1996ne} and the KK-monopole \cite{Cheng:2025efp} solutions, to type IIB geometries with nontrivial axio-dilaton profile.

What we have been discussing is the classical, two-derivative, two field type IIB theory, which is the leading term in the $\alpha'$ expansion of the type IIB string theory.
Under quantum corrections, \eqref{eq:IIB-two-derivative} receives higher order and higher derivative corrections, which can be computed from string perturbation theory and non-perturbative saddles.
It is natural to ask whether such corrections can also be understood from 12d perspective, e.g. at 8-derivatives?
The answer does not appear to be a clearcut yes or no, and the goal of this section is to discuss the current understandings.

\subsection{Type IIB at 4 points}

The 4-point 8-derivative effective action can be written \cite{Liu:2025uqu,Minasian:2015bxa,Policastro:2008hg} as
\begin{equation}
\begin{aligned}
\frac{L_{\text{4pt}}}{\alpha  f_{0}(\tau,\overline{\tau})}
&= t_{8}t_{8} \biggl[R^4+6R^{2}\left(4|\delta\nabla P|^{2}+|\nabla G_{3}|^{2}\right)+24|\delta \nabla P|^{2}|\nabla G_{3}|^{2}\\
&+12R\left(\delta \nabla P(\nabla\overline{G}_{3})^{2}+D\overline{P}(\nabla{G}_{3})^{2}\right)\biggr]\\
&+1536 |\nabla_m P_n \nabla^m P^n|^2\\
&+O_{2}\left((|\nabla G_{3}|^{2})^{2}\right)
\label{eq:PTaction}
\end{aligned}
\end{equation}
where $\alpha = \frac{(\alpha')^3}{3 \cdot 2^{12}}$ and $(\delta \nabla P)_{mrns} \equiv g_{[m[n} \nabla_{r]} P_{s]}$ is defined to have the same symmetries as the Riemann tensor, up to $\delta$-functions located at the sources of $\tau$.
Restricting to the gravity + scalar sector of \eqref{eq:PTaction}, we have
\begin{equation}
\frac{L_{\text{4pt},\tau}}{\alpha f_0(\tau,\overline{\tau})} = t_8t_8
(R^4 + 24 R^2 |\delta \nabla P|^2) + 1536 (\nabla_m P_n \nabla^m P^n)(\nabla_r \overline{P}_s \nabla^r \overline{P}^s).
\label{eq:4pt-gravity-axiodilaton}
\end{equation}
In the 12d perspective $\tau$ is embedded in the metric.
Suppose certain axio-dilaton couplings in the 10d effective action admits a 12d interpretation, one shall be able to rewrite such terms using 12d-covariant differential operators acting on the metric, i.e. the 12d Riemann tensor \eqref{eq:12d-Riemann-complex}. 
Once we had replaced the 10d fields and their derivatives with their 12d counterparts, we may reexamine the resulting expression, and see if the terms group into a natuaral pattern as a result of index splitting.
We had carried out this exercise at the two-derivative level in \eqref{eq:2-derivative-index-splitting}, we now perform the same exercise at the 8-derivative level to \eqref{eq:4pt-gravity-axiodilaton}, as a "bottom-up" approach to review the results of \cite{Minasian:2015bxa}, by arriving at their results in an alternative way.

Let us begin by expanding the $t_8t_8$ contractions.
The $t_8t_8$ contraction with tensors of symmetries of the Riemann tensor is known \cite{Policastro:2008hg} to be 
\begin{equation}
\begin{aligned}
\frac{t_8t_8 R^4}{3 \cdot 2^7}
&=  R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st} + \frac{1}{2}R_{mpnq} R^{qrps} R_{tsur} R^{untm} \\
& - \frac{1}{2}R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv} - \frac{1}{4} R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}\\
& + \frac{1}{16} R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs} + \frac{1}{32}(R_{mnrs} R^{mnrs})^2.
\end{aligned}
\label{eq:t8t8R4}
\end{equation}

Expanding the $t_8 t_8 R^2 |\delta \nabla P|^2$ sector, we find\footnote{
The computation is done with Cadabra, which agrees with the results of \cite{Minasian:2015bxa}. We have taken $f_0(\tau,\overline{\tau})$ to be $2\zeta(3) \tau_2^{3/2}$.
}
\begin{equation}
\begin{aligned}
\frac{1}{3 \cdot 2^{8}\zeta(3) \tau_2^{3/2}}\frac{L_{\text{4-pt},\tau}}{\alpha}
&=  \frac{t_8 t_8 R^4}{3 \cdot 2^7}
+ 4 \nabla_n P_m \nabla^r \overline{P}^s R^{mt}{}_{ru} R^{nu}{}_{st} \\
&+ 4 \nabla_m P_n \nabla^r \overline{P}^s R_{tsur} R^{untm}
+ 4 |\nabla_m P_n \nabla^m P^n|^2 \\
&- 4 \nabla_m P_n \nabla^n \overline{P}^r R_{rsuv} r^{smuv}
+ \frac{1}{2} \nabla_{m} P_{n} \nabla^{m}\overline{P}^{n}R^{rstu}R_{rstu} + O(R^2 P^3).
\end{aligned}
\end{equation}

The next step is to replace the 10d terms with their 12d counterparts. The only 10d terms that remains are $\nabla P$.
we note that because the only 12d Riemann tensor linear in $P$ is $R_{mznz}$ and its conjugate, so we have
\begin{equation}
\widehat{R}_{ambn} \widehat{R}^{a}{}_{r}{}^{b}{}_{s} = 2 \text{Re} D_m P_n D_r \overline{P}_s + O(P^3).
\end{equation}
Substituting this as well as $t_8 t_8 R^4$, we find
\begin{equation}
\begin{aligned}
\frac{1}{3 \cdot 2^{8}\zeta(3) \tau_2^{3/2}}\frac{L_{\text{4-pt},\tau}}{\alpha}
&=
R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st}
+ 2 \widehat{R}_{anbm} \widehat{R}^{arbs} R^{mt}{}_{ru} R^{nu}{}_{st}\\
& + \frac{1}{2}\left[ R_{mpnq} R^{qrps} R_{tsur} R^{untm}
+ 4 \widehat{R}_{ambn} \widehat{R}^{bras} R_{tsur} R^{untm}
+ 2 \widehat{R}_{ambn} \widehat{R}^{bras} \widehat{R}_{csdr} \widehat{R}^{dncm}\right]\\
& - \frac{1}{2}\left[ R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv}
 + 4 \widehat{R}_{mban} \widehat{R}^{anbp} R_{pquv} R^{qmuv} \right]\\
& - \frac{1}{4} R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}\\
& + \frac{1}{16} R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs}\\
& + \frac{1}{32}(R_{rstu} R^{rstu})
\left[R_{mnrs} R^{mnrs}+ 8 \widehat{R}_{ambn} \widehat{R}^{ambn}\right]+ O(\text{5-pt})
\end{aligned}
\label{eq:4pt-gravity-axiodilaton-12d-replaced}
\end{equation}

In this expression we have grouped terms with the same index contraction structure together. 
We again see contraction patterns that could reveal a 12d covariant structure.
For example
\begin{equation}
\widehat{R}_{MNRS}\widehat{R}^{MNRS} = R_{mrns} R^{mnrs} + 4 \widehat{R}_{ambn} \widehat{R}^{ambn} + O(P^3),
\end{equation}
the factor of 4 arises from the 4 ways to choose 2 torus legs in $\widehat{R}_{MNRS}$ that contribute to 4-pt amplitudes.
Hence the last term in \eqref{eq:4pt-gravity-axiodilaton-12d-replaced} is compatible with arising a 12d contraction $\frac{1}{32} (R_{MNRS} R^{MNRS})^2  \in t_8 t_8 \widehat{R}^4$.
Upon further investigation, one finds
\begin{equation}
\begin{aligned}
\widehat{R}_{PNQM} \widehat{R}^{PRQS} \widehat{R}^{MT}{}_{RU} \widehat{R}^{NU}{}_{ST}
&=
R_{pnqm} R^{prqs} R^{mt}{}_{ru} R^{nu}{}_{st}
+ 2 \widehat{R}_{anbm} \widehat{R}^{arbs} R^{mt}{}_{ru} R^{nu}{}_{st}+ \ldots\\
\widehat{R}_{MPNQ} \widehat{R}^{QRPS} \widehat{R}_{TSUR} \widehat{R}^{UNTM}
&= R_{mpnq} R^{qrps} R_{tsur} R^{untm}
+ 4 \widehat{R}_{ambn} \widehat{R}^{bras} R_{tsur} R^{untm}
+ 2 \widehat{R}_{ambn} \widehat{R}^{bras} \widehat{R}_{csdr} \widehat{R}^{dncm}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{RSNP} \widehat{R}_{PQUV} \widehat{R}^{QMUV}
&= R_{mnrs} R^{rsnp} R_{pquv} R^{qmuv}
 + 4 \widehat{R}_{mban} \widehat{R}^{anbp} R_{pquv} R^{qmuv}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{RS}{}_{PQ} \widehat{R}^{QMUV} \widehat{R}^{NP}{}_{UV}
&= R_{mnrs} R^{rs}{}_{pq} R^{qmuv} R^{np}{}_{uv}+ \ldots\\
\widehat{R}_{MNRS} \widehat{R}^{MNPQ} \widehat{R}_{PQUV} \widehat{R}^{UVRS}
&= R_{mnrs} R^{mnpq} R_{pquv} R^{uvrs}+ \ldots\\
(\widehat{R}_{MNRS}\widehat{R}^{MNRS})^2
&= (R_{rstu} R^{rstu})
\left[R_{mnrs} R^{mnrs}+ 8 \widehat{R}_{ambn} \widehat{R}^{ambn}\right]+ \ldots
\end{aligned}
\end{equation}
where the ellipses denote terms with more than 4 fields in 10d, or terms that vanish when summed with the coefficients in \eqref{eq:t8t8R4}.
Thus, every term in \eqref{eq:4pt-gravity-axiodilaton-12d-replaced} has an origin from a 12d contraction $t_8 t_8 \widehat{R}^4$, upon substituting the specific F-theory ansatze \eqref{eq:F-theory-ansatze}.

The relation above was first noted in \cite{Minasian:2015bxa} in a ``top-down" fashion, by making an informed guess of a 12d effective action, then showing that the resulting 10d action matches the known gravity and axio-dilaton amplitudes.
The ``bottom-up" approach outlined here, despite requiring more exercises in index-relabeling and tensor identities, is perhaps more systematic, as it does not require one to make a 12d effective ansatze a priori.
If there were to exist a 12d covariant expression that reproduces any 10d effective action, then after substituting 10d objects for 12d ones, one must find that the terms group into a more natural pattern arising from splitting 12d indices in a covariant expression.
What would be a genuine obstruction to a 12d covariant interpretation, is if certain terms can not be written using covariant 12d objects at all.

\subsection{Type IIB at 5 points: Obstruction to 12d Covariance?}

Recently, the 5-point 8-derivative effective action in the axio-dilaton sector has been computed \cite{Liu:2025uqu}.
Interestingly, in the U(1)-preserving sector at 5 points, there exists a term, which realises SL(2, Z)-invariance on its own, with the form (we drop all numerical factors)
\begin{equation}
L_{\text{5pt},\tau} \supset
\text{Re} R^{mnsr} \nabla_m \overline{P}_s \nabla_n \overline{P}_r P_q P^q.
\label{eq:12d-obstruction}
\end{equation}
Both $R^{mnsr}$ and $\nabla_m \overline{P}_s$ can be written as 12d covariant objects (see \eqref{eq:12d-Riemann-complex}).
However, while we may write $P_q \overline{P}^q$ using $\widehat{R}_{z\overline{z}z\overline{z}}$, there is no 12d covariant object that can be substituted for $P_q P^q$.
We now study this term more carefully.

We had previously worked with, from \eqref{eq:12d-Riemann-complex}, the 12d Riemann tensor components for the complex tangent frame coordinates $\widehat{g}_{zz} = \widehat{g}_{\overline{z}\overline{z}} = 0$, $\widehat{g}_{z\overline{z}} = 1/2$. Using real coordinates where $\widehat{g}_{ab} = \frac{1}{\tau_2}\begin{pmatrix}
1 & \tau_1 \\
\tau_1 & |\tau|^2
\end{pmatrix}$, we find the following components of the 12d Riemann tensor

\medskip
\renewcommand{\arraystretch}{1.8}
\begin{tabular}{c|cccccc}
\toprule
$\widehat{R}_{ambn}$ 
  & $\nabla_m\nabla_n\tau_1$ 
  & $\nabla_m\nabla_n\tau_2$ 
  & $(\nabla_m\tau_1)(\nabla_n\tau_1)$ 
  & $(\nabla_m\tau_2)(\nabla_n\tau_2)$ 
  & $\nabla_m\tau_1\nabla_n\tau_2$ 
  & $\nabla_m\tau_2\nabla_n\tau_1$ \\
\midrule
$\widehat{R}_{1m1n}$ & $0$ & $\frac{1}{2\tau_2^2}$ & $\frac{1}{4\tau_2^3}$ & $-\frac{3}{4\tau_2^3}$ & $0$ & $0$ \\
$\widehat{R}_{1m2n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $-\frac{3\tau_1}{4\tau_2^3}$ & $\frac{1}{4\tau_2^2}$ & $\frac{3}{4\tau_2^2}$ \\
$\widehat{R}_{2m1n}$ & $-\frac{1}{2\tau_2}$ & $\frac{\tau_1}{2\tau_2^2}$ & $\frac{\tau_1}{4\tau_2^3}$ & $-\frac{3\tau_1}{4\tau_2^3}$ & $\frac{3}{4\tau_2^2}$ & $\frac{1}{4\tau_2^2}$ \\

$\widehat{R}_{2m2n}$ & $-\frac{\tau_1}{\tau_2}$ & $\frac{\tau_1^2-\tau_2^2}{2\tau_2^2}$ & $\frac{\tau_1^2-3\tau_2^2}{4\tau_2^3}$ & $\frac{\tau_2^2-3\tau_1^2}{4\tau_2^3}$ & $\frac{\tau_1}{\tau_2^2}$ & $\frac{\tau_1}{\tau_2^2}$ \\
\bottomrule
\end{tabular}
\medskip

As for the rest of the non-vanishing Riemann tensor components,
\begin{equation}
\begin{aligned}
\widehat{R}_{mnab} 
&= 2\widehat{R}_{[a|m|b]n}\\
% = \frac{1}{2\tau_2^2}[\nabla_m\tau_2\nabla_n\tau_1-\nabla_m\tau_1\nabla_n\tau_2],\\
\widehat{R}_{1212}
&= -\frac{1}{2}g^{mn}g^{ab} \widehat{R}_{ambn} 
% = \frac{1}{4\tau_2^2}|\nabla \tau|^2.
\end{aligned}
\end{equation}

Generically $\widehat{R}_{ambn}$, $\widehat{R}_{abcd}$ and $\widehat{R}_{mnab}$ form independent bases for second order derivatives \footnote{We use second order derivative to mean second derivative or products of first derivatives.} of the metric components.
However, for the specific 12d ansatze required by type IIB, $\widehat{R}_{mnab}$ and $\widehat{R}_{abcd}$ can both be obtained as linear combinations or contractions of $\widehat{R}_{ambn}$.
A direct consequence of such lack of independent Riemann tensor components is that there may be second order derivatives of $\tau$ that the 12d Riemann tensor can not capture.
For example, while we can construct $(\nabla \tau_1)^2 + (\nabla \tau_2)^2$ using $\widehat{R}_{1212}$, we can not construct $(\nabla \tau_1)^2 - (\nabla \tau_2)^2$
or $\nabla_m \tau_1 \nabla_n \tau_2$
\footnote{
    Since all nonvanishing 12d Riemann tensors are either pure 10d Riemann tensors or can be obtained via $\widehat{R}_{ambn}$, it suffices to consider linear combinations of $\widehat{R}_{ambn}$, i.e. our table. Demanding no appearances of $\nabla^2 \tau_1$ or $\nabla^2 \tau_2$ enforces $(\nabla \tau_1)^2$ to appear with the same sign as $(\nabla \tau_2)^2$, and that the cross-term $\nabla_m \tau_1 \nabla^m \tau_2$ vanishes.
}
.
Given that
\begin{equation}
P_m P^m = -\frac{1}{4\tau_2^2} 
\left[
    (\nabla\tau_1)^2 - (\nabla\tau_2)^2 + 2i \nabla^m \tau_1 \nabla_m \tau_2
\right],
\end{equation}
the contribution from \eqref{eq:12d-obstruction}, which realizes SL(2, Z) on its own, can not be written in a 12d covariant manner.
We note that the rest of the terms in the U(1)-preseving 5-point effective action in \cite{Liu:2025uqu} do not suffer from this problem.
It was already noted in \cite{Liu:2025uqu} that at 5-pt in the U(1)-preserving sector, certain axio-dilaton couplings begin to deviate from those predicted by $t_8t_8 \widehat{R}^4$.
Our result here is stronger as we have shown that no covariant contraction of any type in 12d, may capture the 5-pt dynamics of type IIB.

\section{Discussion}
We have argued that the answer to whether type IIB effective actions have 12d interpretations is subtle.
While at 4 pts the answer is yes, at 5 pt there exists fundamental obstructions, and this does not have to do with U(1)-violation.
Indeed, it is possible, that beginning at 6-pt or above, there appears additional 12d obstructive terms, similar to the $PP$ described here that together with the 5-pt terms, somehow conspire to support 12d covariant uplift.
To investigate this possibility, one needs axio-dilaton effective actions up to 8 points.
The alternative is that the obstruction we found is real, and type IIB effective actions can not be written in 12d covariant form.
